\section{Requirements}\label{sec:requirements}
\subsection{How to accomplish requirements}\label{subsec:how-to-accomplish-requirements}

\begin{frame}{Solution to problem}
	\setbeamercovered{dynamic} %Makes the text appear before it presents nice!!!!
	\begin{alertblock}{Problems}
		\begin{itemize}
			\item<1-| alert@1> Solution has to be reproducible locally \alert{Exactly as on premises}!
			\item<2-| alert@2> \alert{Infrastructure As Code} Data should be persistent!
			\item<3-| alert@3> \alert{Time consuming} custom configurations per VM!
			\item<4-| alert@4> \item Minimal human interaction \alert{easy to use}!
		\end{itemize}	
	\end{alertblock}
	\begin{exampleblock}{Solutions}
		\begin{itemize}
			\item<1-| alert@1> Introduce IAC elements to solve our problem!
			\item<2-| alert@2> Fully \alert{automated procedure} on every step!
			\item<3-| alert@3> \alert{ADO pipeline} either for Infrastructure or for provisioning VMs!
			\item<4-| alert@4> \alert{Single file} containing all configurations for all VMs!
		\end{itemize}	
	\end{exampleblock}
\end{frame}

\subsection{The correct tool of choice}\label{subsec:the-correct-tool-of-choice}

\begin{frame}{IAC}
	\setbeamercovered{dynamic} %Makes the text appear before it presents nice!!!!
	\begin{alertblock}{Possible Questions}
		\begin{itemize}
			\item<1-| alert@1> Why Ansible?
			\item<2-| alert@2> Why Docker?
			\item<3-| alert@3> Why Terraform?
			\item<4-| alert@4> Why ADO pipelines?
		\end{itemize}	
	\end{alertblock}
	\begin{exampleblock}{Possible Answers}
		\begin{itemize}
			\item<1-| alert@1> Written in Python 2/3 developed and maintained by RedHat!
			\item<2-| alert@2> It gives the ability to control the environment and use persistent volumes!
			\item<3-| alert@3> We can create infinite amount of VMs and keep track of configurations through state file!
			\item<4-| alert@4> We wanted to use a dynamic tool that is easy to use.
		\end{itemize}	
	\end{exampleblock}
\end{frame}
