\section{CI / CD} \label{sec:k8sVagrant}
\subsection{Project smooth CI / CD}

\begin{frame}{Problems / Desires / Solutions on CI / CD}
	\setbeamercovered{dynamic} %Makes the text appear before it presents nice!!!!
	\vspace{-0.4cm}
	\begin{columns}[T] % contents are top vertically aligned
		\begin{column}{5cm} % each column can also be its own environment
			\begin{block}{Assessment Requirements}
				\begin{itemize}
					\item<1-| alert@+> CI / CD (Locally / Remotely).
					\item<2-| alert@+> Everything As a Code
					\item<3-| alert@+> Validation Locally!!!
					\item<4-| alert@+> OS / Inf. dependencies.
				\end{itemize}
			\end{block}
		\end{column}
		\begin{column}{5cm} % alternative top-align that's better for graphics
			\begin{block}{Justification of Requirements}
				\begin{itemize}
					\item<1-| alert@+> Works on my PC, why not on Cloud?
					\item<2-| alert@+> Human error (manual).
					\item<3-| alert@+> Test (automatically).
					\item<4-| alert@+> GitHub Actions, Jenkins
				\end{itemize}
			\end{block}
		\end{column}
	\end{columns}
	\only<5-8>{%
	\begin{block}{Solutions to Requirements}
		\begin{itemize}
			\item<5-| alert@5> Solution has to be reproducible locally. \alert{Exactly as cloud}.
			\item<6-| alert@6> Minimal human interaction. Auto \alert{error handling} (Rollback)!
			\item<7-| alert@7> \alert{Powerful PCs!} (8 CPUs / 35 GB RAM). Browsing (tabs)?
			\item<8-| alert@8> \alert{No Vendor binding} (Azzure DevOps, Jenkins, Bamboo etc).
		\end{itemize}	
	\end{block}
	}%
\end{frame}

\subsection{How to accomplish requirements}

\begin{frame}{Solution to problem}
	\setbeamercovered{dynamic} %Makes the text appear before it presents nice!!!!
	\begin{alertblock}{Problems}
		\begin{itemize}
			\item<1-| alert@1> Solution has to be reproducible locally. \alert{Exactly as cloud}.
			\item<2-| alert@2> Minimal human interaction. Auto \alert{error handling} (Rollback)!
			\item<3-| alert@3> \alert{Powerful PCs!} (8 CPUs / 35 GB RAM). Browsing (tabs)?
			\item<4-| alert@4> \alert{No Vendor binding} (Azzure DevOps, Jenkins, Bamboo etc).
		\end{itemize}	
	\end{alertblock}
	\begin{exampleblock}{Solutions}
		\begin{itemize}
			\item<1-| alert@1> \alert{Containers}. Build / deploy / validate locally (controlled env)!
			\item<2-| alert@2> Fully \alert{automated procedure} on every step!
			\item<3-| alert@3> Launch a \alert{k8s cluster locally} and run all tests locally!
			\item<4-| alert@4> High Level Programming Language with \alert{error handling}!
		\end{itemize}	
	\end{exampleblock}
\end{frame}

\subsection{The correct tool of choice}

\begin{frame}{Ansible}
	\setbeamercovered{dynamic} %Makes the text appear before it presents nice!!!!
	\begin{alertblock}{Possible Questions}
		\begin{itemize}
			\item<1-| alert@1> Why Ansible?
			\item<2-| alert@2> Are there any benefits of this tool?
			\item<3-| alert@3> Ansible works on ssh how it will work locally?
			\item<4-| alert@4> How it can interact with Containers, k8s, Cloud, tests?
		\end{itemize}	
	\end{alertblock}
	\begin{exampleblock}{Possible Answers}
		\begin{itemize}
			\item<1-| alert@1> Written in Python 2/3. Developed and maintained by RedHat.
			\item<2-| alert@2> Woks perfectly without extra configurations on all OS.
			\item<3-| alert@3> It can be configured to run on localhost without ssh session.
			\item<4-| alert@4> It has infinite amount of packages for OS, Containers, Cloud.
		\end{itemize}	
	\end{exampleblock}
\end{frame}